Current model cost effect

### 2020-09-30 src/current_model_effect.Rmd
plotting device improved

---
title: "Current model cost effect"
author: "Esa Turkulainen & Mikko Arvas"
date: "`r Sys.time()`"
output:
  pdf_document: default
  html_document: default
---

@@

size <- 2
p <- ggplot(tprs.plot)
p <- p + geom_line(aes(x=probability,y=value,col=name)) + ylab("Cost effect (€ / donation)") + xlab("Probability of deferral cut-off") + labs(color="Deferral length (mo)")
p <- p + geom_point(aes( y =tprs$E6[which(tprs$E6 == min(tprs$E6))] , x = tprs$probability[which(tprs$E6 == min(tprs$E6))] ))
p <- p + geom_label(aes( y =tprs$E6[which(tprs$E6 == min(tprs$E6))] , x = tprs$probability[which(tprs$E6 == min(tprs$E6))] , label = paste0("p>=",round(tprs$probability[which(tprs$E6 == min(tprs$E6))],2) , " ; ",  round(tprs$E6[which(tprs$E6 == min(tprs$E6))],2)," €")), nudge_y=0.2,size=size)
p <- p + geom_point(aes( y =tprs$E12[which(tprs$E12 == min(tprs$E12))] , x = tprs$probability[which(tprs$E12 == min(tprs$E12))] ))
p <- p + geom_label(aes( y =tprs$E12[which(tprs$E12 == min(tprs$E12))] , x = tprs$probability[which(tprs$E12 == min(tprs$E12))] , label = paste0("p>=",round(tprs$probability[which(tprs$E12 == min(tprs$E12))],2) , " ; ",  round(tprs$E12[which(tprs$E12 == min(tprs$E12))],2)," €")), nudge_y=0.2,size=size)
p <- p + theme(legend.position="bottom")
p
ggsave(filename="../results/cme_prob_cut_curve.pdf", p, width = 90,  height = 80,units="mm", dpi=600, scale=1.0,encoding = "ISOLatin9.enc")
```

@@

```{r ,warning=FALSE}
#Get the a (y) and q (x) mappings for the optimised 6 and 12 month scenarios
x6 <- head(which(q.seq > tprs$q[which(tprs$E6 == min(tprs$E6))] ),1)
y6 <- head(which(adjustments > tprs$a6[which(tprs$E6 == min(tprs$E6))]),1)
x12 <- head(which(q.seq > tprs$q[which(tprs$E12 == min(tprs$E12))] ),1)
y12 <- head(which(adjustments > tprs$a12[which(tprs$E12 == min(tprs$E12))]),1)
#Plot them
colnames(E.long) <- c("adjustment", "q", "cost")
p <- ggplot(E.long, aes(x = q, y = adjustment, z = cost)) +
  geom_tile(aes(fill=cost)) +
  stat_contour(color = "white", size = 0.7, binwidth =  1) +
  scale_fill_gradientn(colours=c("blue", "red")) +
  labs(x="q% i.e. deferral rate", y=expression(a[tot]~i.e.~donation~interval~coefficient ))  + 
  theme_bw() +
  scale_x_continuous(breaks = c(1, 1001), labels = c("0", "3.2")) +
  scale_y_continuous(breaks = c(1, 1001), labels = c(as.character(min(adjustments)), as.character(max(adjustments))))
#Add numeric values of costs with optimised classifier probability cut-offs
p <- p + annotate("text" ,
                  x = x6 , 
                  y = y6 - 50,
                  label = paste0("6 mo: ", round(tprs$E6[which(tprs$E6 == min(tprs$E6))],2),' (',round(deframe(p6.ci[4,2]),2)," - ",round(deframe(p6.ci[4,3]),2),') €'  ),
                  colour = "white")

p <- p + annotate("text" ,
                  x = x12 , 
                  y = y12 - 50,
                  label = paste0("12 mo: ", round(tprs$E12[which(tprs$E12 == min(tprs$E12))],2),' (',round(deframe(p8.ci[5,2]),2)," - ",round(deframe(p8.ci[5,3]),2),') €'  ),
                  colour = "white")
#Add points estimates
p <- p + annotate("point", x = x6, y = y6, colour = "white", size = 3, alpha = 1) 
p <- p +  annotate("point", x = x12, y = y12, colour = "white", size = 3, alpha = 1)

@@

p <- p + labs(fill="Cost effect (€ / donation)")  + theme(legend.position="bottom")
p
ggsave(filename="../results/cme_cost_surface_werr.pdf",  width = 180,  height = 120,units="mm", dpi=600, scale=1.0,encoding = "ISOLatin9.enc")
```

>>>>

---
title: "Current model cost effect"
author: "Esa Turkulainen & Mikko Arvas"
date: "`r Sys.time()`"
output:
  pdf_document: default
  html_document: default
dev: cairo_pdf 
---

@@

size <- 2
p <- ggplot(tprs.plot)
p <- p + geom_line(aes(x=probability,y=value,col=name)) + ylab("Cost effect (€ / donation)") + xlab("Probability of deferral cut-off") + labs(color="Deferral length (mo)")
p <- p + geom_point(aes( y =tprs$E6[which(tprs$E6 == min(tprs$E6))] , x = tprs$probability[which(tprs$E6 == min(tprs$E6))] ))
p <- p + geom_label(aes( y =tprs$E6[which(tprs$E6 == min(tprs$E6))] , x = tprs$probability[which(tprs$E6 == min(tprs$E6))] , label = paste0("p>=",round(tprs$probability[which(tprs$E6 == min(tprs$E6))],2) , " ; ",  round(tprs$E6[which(tprs$E6 == min(tprs$E6))],2)," €")), nudge_y=0.2,size=size)
p <- p + geom_point(aes( y =tprs$E12[which(tprs$E12 == min(tprs$E12))] , x = tprs$probability[which(tprs$E12 == min(tprs$E12))] ))
p <- p + geom_label(aes( y =tprs$E12[which(tprs$E12 == min(tprs$E12))] , x = tprs$probability[which(tprs$E12 == min(tprs$E12))] , label = paste0("p>=",round(tprs$probability[which(tprs$E12 == min(tprs$E12))],2) , " ; ",  round(tprs$E12[which(tprs$E12 == min(tprs$E12))],2)," €")), nudge_y=0.2,size=size)
p <- p + theme(legend.position="bottom")
p
#ggsave(filename="../results/cme_prob_cut_curve.pdf", p, width = 90,  height = 80,units="mm", dpi=600, scale=1.0,encoding = "ISOLatin9.enc")
ggsave(filename="../results/cme_prob_cut_curve.pdf", p, width = 90,  height = 80,units="mm", dpi=600, scale=1.0,device=cairo_pdf)
```

@@

```{r ,warning=FALSE}
#Get the a (y) and q (x) mappings for the optimised 6 and 12 month scenarios
x6 <- head(which(q.seq > tprs$q[which(tprs$E6 == min(tprs$E6))] ),1)
y6 <- head(which(adjustments > tprs$a6[which(tprs$E6 == min(tprs$E6))]),1)
x12 <- head(which(q.seq > tprs$q[which(tprs$E12 == min(tprs$E12))] ),1)
y12 <- head(which(adjustments > tprs$a12[which(tprs$E12 == min(tprs$E12))]),1)
#Plot them
colnames(E.long) <- c("adjustment", "q", "cost")
p <- ggplot(E.long, aes(x = q, y = adjustment, z = cost)) +
  geom_tile(aes(fill=cost)) +
  stat_contour(color = "white", size = 0.7, binwidth =  1) +
  scale_fill_gradientn(colours=c("blue", "red")) +
  labs(x="q% i.e. rate of avoided deferrals", y=expression(a[tot]~i.e.~donation~interval~coefficient ))  + 
  theme_bw() +
  scale_x_continuous(breaks = c(1, 1001), labels = c("0", "3.2")) +
  scale_y_continuous(breaks = c(1, 1001), labels = c(as.character(min(adjustments)), as.character(max(adjustments))))
#Add numeric values of costs with optimised classifier probability cut-offs
p <- p + annotate("text" ,
                  x = x6 , 
                  y = y6 - 50,
                  label = paste0("6 mo: ", round(tprs$E6[which(tprs$E6 == min(tprs$E6))],2),' (',round(deframe(p6.ci[4,2]),2)," – ",round(deframe(p6.ci[4,3]),2),') €'  ),
                  colour = "white")

p <- p + annotate("text" ,
                  x = x12 , 
                  y = y12 - 50,
                  label = paste0("12 mo: ", round(tprs$E12[which(tprs$E12 == min(tprs$E12))],2),' (',round(deframe(p8.ci[5,2]),2)," – ",round(deframe(p8.ci[5,3]),2),') €'  ),
                  colour = "white")
#Add points estimates
p <- p + annotate("point", x = x6, y = y6, colour = "white", size = 3, alpha = 1) 
p <- p +  annotate("point", x = x12, y = y12, colour = "white", size = 3, alpha = 1)

@@

p <- p + labs(fill="Cost effect (€ / donation)")  + theme(legend.position="bottom")
p
#ggsave(filename="../results/cme_cost_surface_werr.pdf",  width = 180,  height = 120,units="mm", dpi=600, scale=1.0,encoding = "ISOLatin9.enc")
ggsave(filename="../results/cme_cost_surface_werr.pdf",  width = 180,  height = 120,units="mm", dpi=600, scale=1.0, device=cairo_pdf)
#check this from the performance plot
```
